Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2023-10-25 Unicode.Implimentation.tex
Add files via upload
Add initial RXU information

\makeindex[intoc]
\setmainfont{CMU Serif}
% texlive-cm-unicode or retrieve cm-unicode with MikTex Console

@@

Assuming that the width is in in terms of octets
\begin{lstlisting}[
    caption={c2x() with width parameter},%
    linewidth=35em%
    ]
    foo = 'Ren!\'{e}!'
    bar = foo~UTF-8
    /* assumes that width parameter is in octets */
    say foo~c2x(2) /* Displays 00520065006E00E9  */
    say bar~c2x    /* Displays 52656EC3A9        */
\end{lstlisting}

@@

@@

RXU has five tpes of string literals:
\begin{definition}
\item['string'] The type is determined by OPTIONS.
\item['string'P] Unicode by code point
\item['string'T] Unicode by EGC
\item['space separated tokens'U] Unicode code points by alias, name or value
\item['string'Y] Legacy bYte string
\end{definition}

@@

\printbibliography[%
    keyword=ARB,%
    title={GitHub ARB documents}%
    ]
\printbibliography[%
    keyword=FAQ,%
    title=FAQs%
    ]
\printbibliography[%
    keyword=standard,%
    notkeyword=FAQ,%
    title={Official documents}%
    ]

>>>>

\defbibcheck{standard}{\iffieldequalstr{type}{standard}{}{\skipentry}}

\makeindex[intoc]

\setmainfont{CMU Serif}
% texlive-cm-unicode or retrieve cm-unicode with MikTex Console

@@

Assuming that the width is in in terms of octets
\begin{lstlisting}[%
    caption={c2x() with width parameter},%
    linewidth=35em%
    ]
    foo = 'Ren!\'{e}!'
    bar = foo~UTF-8
    /* assumes that width parameter is in octets */
    say foo~c2x(2) /* Displays 00520065006E00E9  */
    say bar~c2x    /* Displays 52656EC3A9        */
\end{lstlisting}

@@

\subsection{RXU c2x() and c2u()}
In RXU, \textbf{c2x()} for Unicode code point strings returns the
hexadecimal values of UTF-8 sequences rather than the hexadecimal
values of unicode scalars. The second parameter of \textbf{c2u()}
controls the output format, and \textbf{c2x(foo,UTF-32)} returns space
separated Unicode scalars.

@@

RXU has five types of string literals:
\begin{definition}
\item['string'] The type is determined by OPTIONS.
\item['string'P] Unicode by code point
\item['string'T] Unicode by EGC
\item['space separated tokens'U]
Unicode code points by alias, name or hexadecimal value;
the string is BYTES rather than CODEPOINTS or TEXT.
\item['string'Y] Legacy bYte string
\end{definition}

@@

\printbibliography[%
    keyword=ARB,%
    title={GitHub ARB documents}%
    ]
\printbibliography[%
    keyword=FAQ,%
    title=FAQs%
    ]
\printbibliography[%
    check={standard},%
    notkeyword={FAQ},%
    title={Official documents}%
    ]
